Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
prune metric section

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $T=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
to inferred have around 15000 edge or a density of $0.15\%$ and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

% Metrics : ROC AUC and AUPRC
The network inference task can be viewed as a binary classification task
where one has to correctly classified the presence or the absence of edges
of the graph. Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$,
the connectivity score matrix $\hat{y}_{i,j} \in \mathcal{R}$
and threshold value $\tau$, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = n - tp(\tau) - tn(\tau) -fn(\tau)$.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
as a function of the false positive rate
$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$.  As suggested in
\cite{schrynemackers2013protocols},
we also compare the same methods with the area under the precision-recall
curve (AUPRC) obtained by varying the threshold
$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
in section (todo ref).
Since  there is no self connection (neuron connected to itself), we set
the diagonal elements of $\hat{y}_{i,j}$ to the minimum prior evaluation.

>>>>

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets are time series of size $T=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
to inferred have around 15000 edge and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

% Metrics : ROC AUC and AUPRC
In supervised learning term, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not E, \forall i \in V$) and some inference methods could spuriously
leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson correlation,
we set those elements to the minimum of $\hat{A}$ prior evaluating those
algorithms.
